---
title: "ILL Summary of OA Sources"
author: "Jessica Minnier"
date: '`r Sys.Date()`'
output:   
  github_document:
    toc: yes
  html_document:
    code_folding: hide
    highlight: pygments
    keep_md: no
    number_sections: yes
    smart: yes
    theme: yeti
    toc: yes
    toc_float: yes
---


```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(skimr)
library(janitor)
library(jmmisc)
library(here)
#### Global chunk options -----------------------------

knitr::opts_chunk$set(
  eval       = TRUE,    # whether to run code in code chunk
  include    = TRUE,    # whether to include the chunk output
  echo       = FALSE,   # Whether to show code chunk in final output
  error      = TRUE,    # whether to display error messages
  message    = FALSE,   # whether to preserve messages
  warning    = FALSE,   # whether to preserve warnings
  comment    = "#>",    # a character string to append at start
                        # of each line of results in final document
  tidy       = FALSE,   # whether to tidy code chunks for display
  dpi        = 96, 
  fig.width  = 6,       # consistent width for figures
  fig.asp    = 0.618,   # the golden ratio, can be adjusted in individual chunks
  out.width  = "100%",   # controls the output size
  fig.align  = "center" # give plot room to breathe
)
```

```{r, echo=FALSE}
source(here("code","01-pull_oabutton_data.R"))
res_oabutton <- res
source(here("code","01-pull_unpaywall_data.R"))
res_unpaywall <- res
res <- left_join(res_unpaywall,res_oabutton)
```

# Table of OA Results

## OA Button

```{r}
res %>% tabyl(oabutton_oa_result) %>% adorn_totals() %>% adorn_pct_formatting()
```

```{r}
res %>% ggplot(aes(x=institution,fill=oabutton_oa_result)) + 
  geom_bar(position = "dodge") + 
  theme_minimal()
```

## Unpaywall

```{r}
res %>% tabyl(unpaywall_oa_result) %>% adorn_totals() %>% adorn_pct_formatting() 
```

```{r}
res %>% ggplot(aes(x=institution,fill=unpaywall_oa_result)) + geom_bar(position = "dodge") + 
  theme_minimal()
```


## Crosstab

Note OA button found some OA articles that did not have a doi, as well as some articles that had a doi. Unpaywall just found a few extra articles.

Below is % ($n$) where % is percent of total number of queries `r nrow(res)` and $n$ is number of queries. The columns are unpaywall results and the rows are OA button results.

```{r}
res %>% tabyl(oabutton_oa_result, unpaywall_oa_result) %>% 
  adorn_totals(where = c("row","col")) %>%
  adorn_percentages(denominator = "all") %>%
  adorn_pct_formatting() %>% 
  adorn_ns() %>%
  adorn_title("combined") 
```

As a proportion of queries with a DOI:

```{r}
res %>% 
  filter(doi_present==1) %>%
  tabyl(oabutton_oa_result, unpaywall_oa_result) %>% 
  adorn_totals(where = c("row","col")) %>%
  adorn_percentages(denominator = "all") %>%
  adorn_pct_formatting() %>% 
  adorn_ns() %>%
  adorn_title("combined") 
```




```{r}
res %>% ggplot(aes(x=oabutton_oa_result,fill=unpaywall_oa_result)) + geom_bar() + 
  theme_minimal() + ggtitle("OA Button results, by Unpaywall results")

res %>% ggplot(aes(x=oabutton_oa_result,fill=unpaywall_oa_result)) + geom_bar(position = "fill") +
  ylab("Proportion")+
  theme_minimal() + ggtitle("OA Button results, showing proportion of Unpaywall results")
```

# Total found

```{r}
res %>% 
  mutate(oa_by_either_method = 
                 ifelse(
                   (unpaywall_oa_result=="oa_found")|(oabutton_oa_result=="oa_found"), "oa_found", "oa_not_found")) %>%
  tabyl(oa_by_either_method) %>% adorn_totals() %>% adorn_pct_formatting()
                   
```


